On the Synchronization Power of Openflow Data Plane

### 2015-03-13 inband-STN.tex

We assume that every transaction has a unique identifier. 
Every operation within a transaction generates a number of  OpenFlow
messages using \textsc{FlowMod} commands.
We therefore assume that each of these OpenFlow messages is marked as  a \emph{bundle} message,
where the transaction's identifier is used as the bundle id.

@@

\section{Implementing $\textit{CAS}$ with FlowMod commands}
\begin{algorithm}[H]
    \caption{$\textit{CAS}(old,new)$}
    \label{alg:cas2}
    \begin{algorithmic}[1]
    %\Require  id $i$.
%    \Ensure
			\State $cmds \gets new\ list()$
    		\State $value \gets  old$
    		\State $mask \gets  all-1$
    		\State $match \gets (value,mask)$
    		%\State $cookie \gets x\concat self$
    		\State $action \gets 2$
    		\State $flag \gets OFPFF\_CHECK\_OVERLAP$
    		\State $cmd1\gets \textsc{FlowMod}(match, op = ADD, flag, action) $
    		\State $cmd2\gets \textsc{FlowMod}(match, op = DELETE) $
    		\State $cmd3\gets \textsc{FlowMod}(cookie = old, op = DELETE) $
    		\State $cmds.append(cmd1)$
    		\State $cmds.append(cmd2)$
    		\State $cmds.append(cmd3)$
    		\State $range\_matches \gets EncodeRange([0,new-1])\cup EncodeRange([new+1,MAX\_ID])$
    		\For {$r\_match \in range\_matches $}
    		    		\State $cookie \gets new$
    		    		\State $action \gets 1$
    		    		\State $flag \gets 0$
    		    		\State $cmd\gets \textsc{FlowMod}(r\_match, ADD, flag, cookie, action) $
    		    		\State $cmds.append(cmd)$
    		\EndFor
			\Return $cmds$
    \end{algorithmic}
\end{algorithm}

>>>>

We assume that every transaction has a unique identifier. 
Every operation within a transaction generates a number of  OpenFlow
messages. Each of the messages can be wrapped 
is marked as a 
in a \emph{bundle} message
%,where the transaction's identifier is used as the bundle id. 
.
Each bundle message carries a bundle id, where messages with same bundle id are considered to belong to same bundle and are performed atomically.

%The OpenFlow messages that we use (besides )

@@

\section{Implementing $\textit{CAS}$ with FlowMod commands}

Here we describe a second implementation of the Compare\&Set abstraction that is based on entirely on flow entry creations and deletions (FlowMod commands).

\begin{algorithm}[H]
    \caption{$\textit{CAS}(old,new)$}
    \label{alg:cas2}
    \begin{algorithmic}[1]
    %\Require  id $i$.
%    \Ensure
			\State $cmds \gets new\ list()$
    		\State $value \gets  old$
    		\State $mask \gets  all-1$
    		\State $match \gets (value,mask)$
    		%\State $cookie \gets x\concat self$
    		\State $action \gets 2$
    		\State $flag \gets OFPFF\_CHECK\_OVERLAP$
    		\State $cmd1\gets \textsc{FlowMod}(match, op = ADD, flag, action) $
    		\State $cmd2\gets \textsc{FlowMod}(match, op = DELETE) $
    		\State $cmd3\gets \textsc{FlowMod}(cookie = old, op = DELETE) $
    		\State $cmds.append(cmd1)$
    		\State $cmds.append(cmd2)$
    		\State $cmds.append(cmd3)$
    		\State $range\_matches \gets EncodeRange([0,new-1])\cup EncodeRange([new+1,MAX\_ID])$
    		\For {$r\_match \in range\_matches $}
    		    		\State $cookie \gets new$
    		    		\State $action \gets 1$
    		    		\State $flag \gets 0$
    		    		\State $cmd\gets \textsc{FlowMod}(r\_match, ADD, flag, cookie, action) $
    		    		\State $cmds.append(cmd)$
    		\EndFor
			\Return $cmds$
    \end{algorithmic}
\end{algorithm}
